Schramm-Loewner evolution in tricritical Ising model

### 2013-06-25 AffineLieAlgebras/Simons/paper.tex
Added some text and acknoledgements

Tricritical Ising model was introduced as a modification of the Ising model \cite{}. The model is
the dilute Ising model with the Hamiltonian 
\begin{equation}
  \label{eq:1}
  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2.
\end{equation}
Here $\mu$ is chemical potential of vacancies,
if $\mu$ tends to zero we recover ordinary Ising model without vacant sites. We consider the model on some domain
$\Omega$ in complex plane. The model has three vacuum states with the spins on all sites equal to
$+1$, $-1$ and $0$. In tricritical point the vacuum is degenerate.

@@

@@

>>>>

Tricritical Ising model was introduced as a modification of the Ising model \cite{} (See Malte Henkel ``Conformal invariance and critical phenomena'' 430, 408). (pp 14, 221, 340).

Blume-Capel model. Critical exponents [430]. Mathematica program for CFT: Lassig Mussardo CPC 66, 71 (1991) [423].

 The model is
the dilute Ising model with the Hamiltonian 
\begin{equation}
  \label{eq:1}
  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2.
\end{equation}
Here $\mu$ is chemical potential of vacancies,
if $\mu$ tends to zero we recover ordinary Ising model without vacant sites. We consider the model on some domain
$\Omega$ in complex plane. The model has three vacuum states with the spins on all sites equal to
$+1$, $-1$ and $0$. In tricritical point the vacuum is degenerate.

@@

Bolzmann weights are
\begin{equation}
  \label{eq:4}
    \begin{array}{lllll}
    V_{-} &=& W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      1 & 2
    \end{array}\right| u \right) &=&   W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      3 & 2
    \end{array}\right| u
\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
\end{equation}

@@

\section*{Acknowledgements}
\label{sec:acknowledgements}

This research was started during my stay at Simons center for geometry and physics in Stony Brook
university. I thank Simons foundation for the financial support during my stay, the organizers of
the program ``Conformal geometry'' and Simons center staff for their hospitality. I also thank
Christian Hagendorff(?) and Dmitry Chelkak for fruitful discussions.

This work  is supported by
the Chebyshev Laboratory (Department of Mathematics and Mechanics,
Saint-Petersburg State University) under the grant 11.G34.31.0026
of the Government of the Russian Federation and by the Dynasty foundation.

I am grateful to my wife Alexandra for her constant support and care.
